Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd

>>>>

## Population {#population}

The “population” variable in the dataset represents the status of each
entry. it is the abbreviated description of the respondent group, categorizing
participants as “lv” (likely voters) or “rv” (registered voters). They represent
different levels of participation and potential voting behavior. Likely voters
are individuals who are not only registered but are statistically more likely
to vote based on historical data or survey responses. In contrast, registered
voters include all individuals who are eligible to vote, regardless of their
likelihood of participation.
